---
title: "Happiness Rink in 2017-2019"
output:
  html_document:
    fig_caption: false
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
---

```{r setup, include=FALSE}


knitr::opts_chunk$set(echo = TRUE)
options(digits = 7)

library(tidyverse)
library(Hmisc)
library(corrplot)
library(rio)
library(tinytex)
library(ggplot2)
library(dplyr)
library(MASS)
library(knitr)
library(DT)
library(plyr)

```


```{r output="asis",  echo=FALSE, , include=FALSE}
## Read data
happiness2019 <- read_csv ("data/2019.csv")
happiness2018 <- read_csv ("data/2018.csv")
happiness2017 <- read_csv ("data/2017.csv")
```

```{r echo=FALSE, , include=FALSE}
# Add a nenw column for year
happiness2019$year <- c(2019)
happiness2018$year <- c(2018)
happiness2017$year <- c(2017)

```

```{r output="asis",  echo=FALSE, , include=FALSE}
# Rename column to easir join it
colnames(happiness2019)[1] <- "Rank"
colnames(happiness2019)[4] <- 'Economy'
colnames(happiness2019)[6] <- 'Healthy'
colnames(happiness2019)[7]<- "Freedom"
colnames(happiness2019)[9]<- "Government corruption"

#head(happiness2019)
```

```{r output="asis",  echo=FALSE, , include=FALSE}

colnames(happiness2018)[1] <- "Rank"
colnames(happiness2018)[4] <- 'Economy'
colnames(happiness2018)[6] <- 'Healthy'
colnames(happiness2018)[7]<- "Freedom"
colnames(happiness2018)[9]<- "Government corruption"

happiness2018$`Government corruption`  <- as.numeric(happiness2018[[9]])

#head(happiness2018)



```



```{r echo=FALSE}
colnames(happiness2017)[1] <- "Country or region"
colnames(happiness2017)[2] <- "Rank"
colnames(happiness2017)[3] <- "Score"
colnames(happiness2017)[6] <- 'Economy'
colnames(happiness2017)[8] <- 'Healthy'
colnames(happiness2017)[7]<- "Freedom"
colnames(happiness2017)[11]<- "Government corruption"
#as.numeric(unlist(happiness2017))
#head(happiness2017)
```


```{r output="asis",  echo=FALSE}

# combine the happiness data in 2018 and 2019
happiness <- rbind.fill(happiness2017,happiness2018, happiness2019) 

```

## Correlation Matrix

```{r echo=FALSE , include=FALSE}

happiness_cm <- happiness[,c(3,6,7,8,9,12)]
happiness.cor = cor(happiness_cm)
#compute Spearman  coefficients

happiness.cor = cor(happiness_cm, method = c("spearman"))

happiness.rcorr = rcorr(as.matrix(happiness_cm))
happiness.rcorr

happiness.coeff <- happiness.rcorr$r
happiness.p <- happiness.rcorr$P




```

### visualizing the correlation matrix
```{r output="asis",  echo=FALSE}
#Visualizing the correlation matrix
corrplot(happiness.cor)
```

### Correlated valeu to each other
```{r output="asis",  echo=FALSE}
newdatacor = cor(happiness[c(3,6,7,8,9,12)])
corrplot(newdatacor, method = "number")
```

## Scatter plot 
### Happiness Score Vs Economy
```{r output="asis",  echo=FALSE }
ggplot(subset(happiness), aes(x = Economy , y = Score)) + 
  geom_line(color = "steelblue", size = 1) +
  geom_point(color = "steelblue")+
   
  geom_smooth(aes(color = year, fill = year), 
              method = "lm", fullrange = TRUE) +
  facet_wrap(~ year) +
  theme_bw() 
```

### Happiness Score Vs Healthy
```{r output="asis",  echo=FALSE}
ggplot(subset(happiness), aes(x = Healthy , y = Score)) + 
  geom_line(color = "steelblue", size = 1) +
  geom_point(color = "steelblue")+
   
  geom_smooth(aes(color = year, fill = year), 
              method = "lm", fullrange = TRUE) +
  facet_wrap(~ year)
```

### Happiness Score Score Vs Freedom
```{r output="asis",  echo=FALSE}
ggplot(subset(happiness), aes(x = Freedom  , y = Score)) + 
  geom_line(color = "steelblue", size = 1) +
  geom_point(color = "steelblue")+
   
  geom_smooth(aes(color = year, fill = year), 
              method = "lm", fullrange = TRUE) +
  facet_wrap(~ year) +
  theme_bw()
```



```{r output="asis",  echo=FALSE}
happiness_t <- happiness %>% 
  pivot_longer(-c(`Country or region`)) %>% 
  group_by(name) %>% 
  mutate(Z_score = scale(value))
```

##  Distributions by the Z_score

```{r output="asis",  echo=FALSE}
ggplot(happiness_t, aes(Z_score)) +
  geom_density() +
  facet_grid(name ~ .)
```


## Describe Economy, Healthy, and Freedom

### Economy
```{r output="asis",  echo=FALSE}

des_e <- describe(happiness$Economy)
des_e 
   
```

### Healthy
```{r output="asis",  echo=FALSE}

des_h <- describe(happiness$Healthy)
des_h
     
```

### Freedom
```{r output="asis",  echo=FALSE}

des_f <- describe(happiness$Freedom)
 des_f
     
```

## Descriptive Statistics

```{r output="asis",  echo=FALSE}
happiness %>% 
  group_by(year) %>%
  summarise(n = length(year), Average = mean(Score) ,SD= sd(Score) )%>%
       kable()
```
## Plot The mean of Score
```{r output="asis",  echo=FALSE}
ggplot(happiness, aes(year,Score)) +
     geom_jitter(width = 0.15) +
     stat_summary(fun.data = mean_sdl, 
                  fun.args = list(mult = 1),
                col = "red")
```

## Inferential Statistics

### The one-way ANOVA summary:

```{r output="asis", echo=FALSE}

   happiness_lm <- lm(Score ~ year , data =  happiness)
     anova(happiness_lm) %>%
       kable()

```


 

